% !TEX program = xelatex
% This is my resume
% by ice1000

\documentclass{resume}

% \usepackage{lastpage}
% \usepackage{fancyhdr}
\usepackage{linespacing_fix} % disable extra space before next section

\begin{document}
% \pagestyle{fancy}
% \fancyhf{}
% \renewcommand\headrulewidth{0pt}
% \cfoot{\thepage\ of \pageref{LastPage}}

\name{Tesla Ice Zhang}

\basicInfo{
  \email{ice1000kotlin@foxmail.com} \textperiodcentered\
  \phone{(1) 717-728-6526} \textperiodcentered\
  \github[ice1000]{https://github.com/ice1000} \textperiodcentered\
  \homepage{https://ice1000.org}
  % \linkedin[user]{https://www.linkedin.com/in/user}
}

\section{Education}
\datedsubsection{\textbf{The Pennsylvania State University (PSU)}, PA, US}{08/2018 -- Current}
  Major: Computer Science, Anticipated Graduation Date: 06/2022, GPA 3.20/4.00

\section{Work Experience}
\datedsubsection{\textbf{Sourcebrella Inc.}, Shenzhen, China}{02/2018 -- 07/2018}
\role{Static Analysis}{Compiler Front-End, IDE Plugin Dev Intern}
\begin{itemize}
  \item Created IntelliJ/CLion/Eclipse plugin for the Pinpoint analyzer. Co-worked on the SonarQube plugin.
  \item Created a multi-threading cross Java/Kotlin source code indexer which can index Hadoop within 4 minutes.
  % \item Learned a lot about Linux programming and Clang/LLVM.
\end{itemize}

\datedsubsection{\textbf{PingCAP}, Remote}{08/2018 -- 08/2019}
\role{Distributed Storage Systems}{TiKV Intern - Ecosystem Team}
\begin{itemize}
  \item Improved many TiKV libraries, like
    optimizing the performance of
    \href{https://docs.rs/crate/grpcio} {grpcio},
    adding new features to
    \href{https://docs.rs/crate/procinfo} {procinfo}.
  \item Helped to migrate the Protocol-Buffer library used by TiKV and its Raft implementation.
\end{itemize}

\datedsubsection{\textbf{JetBrains}, Remote}{01/2020 -- Present}
\role{HoTT and Dependent Types}{Theorem Prover Dev Intern}

\section{Personal Projects}
% \datedsubsection{\textbf{FriceEngine}}{\url{https://icela.github.io/}}
% % \role{Kotlin, C\#, Racket, Ruby}{Founder and main contributer to the Kotlin/C\#/Ruby version}
% A multilingual, natively-written, easy-to-use game engine series.
% \begin{itemize}
%   \item Based on life cycle / utility APIs, based on each languages' built-in GUI framework,
%     easy to install.
%   \item GitHub issues / milestones are used as task / version managing tools, nice changelogs.
%   \item A JavaFX-based drag-and-drop GUI designer, generates multilingual codes for each language.
% \end{itemize}

% \datedsubsection{\textbf{DevKt}}{\url{https://github.com/ice1000/dev-kt}}
% Cross-platform lightweight code editor / Kotlin IDE
% \begin{itemize}
  % \item Built-in Java/Kotlin highlights and completion, that can support other languages
    % via plugins (transplantable from JetBrains IDE's).
    % Has extra build \& run support for Kotlin.
  % \item Flexible architecture, decoupled high-level logic with UI, migration to other UI frameworks is easy.
  % \item Provides fine-grained highlight color and keymap settings, supports hot reload.
% \end{itemize}

\datedsubsection{\textbf{Voile}}{\url{https://github.com/owo-lang/voile-rs}}
Experimental dependently-typed programming language with row-polymorphism
\begin{itemize}
  \item Supports dependent types, meta variable unification, and non-dependent row-polymorphic record and variant.
  \item Supports cumulative universe levels and uses a universe lifting operation to get rid of Set$\omega$.
  \item Implements CLI parser / source code parser and interactive REPL with the help of Rust language's ecosystem.
\end{itemize}

% \datedsubsection{\textbf{minitt-rs}}{\url{https://github.com/owo-lang/minitt-rs}}
% Experimental dependently-typed programming language, based on \href{http://www.cse.chalmers.se/~bengt/papers/GKminiTT.pdf} {Mini-TT}
% \begin{itemize}
  % \item Supports $\Pi$ types (return type depends on input value), $\Sigma$ types (tuple's members' type depend on members' values), sum types and case-split.
  % \item Extendes the type system with subtyping on first-class sum types while still supports recursive types.
  % \item Implements CLI parser / source code parser and interactive REPL with the help of Rust language's ecosystem.
% \end{itemize}

% \datedsubsection{\textbf{Lice language}}{\url{https://github.com/lice-lang/lice}}
% \role{Kotlin, Java}{Founder and main contributer}
% Scalable programming language running on JVM
% \begin{itemize}
  % \item Supports lambda with and lazy (call by need)/macro (call by name)/strict (call by value).
  % \item About 1/20 of Java's (Hotspot 8u151) performance, provides Java interaction and script engine support.
  % \item Provides CLI REPL with GHCi-style code completion/colored output and JetBrains.
    % IDE plugin supporting semantic-based highlights, completion, go-to-definition, rename, eval-and-replace, quick fixes, etc.
% \end{itemize}

\datedsubsection{\textbf{IntelliJ Pest}}{\url{https://github.com/pest-parser/intellij-pest}}
Pest (parser generator written in Rust) plugin for JetBrains IDEs
\begin{itemize}
  \item Semantic-based highlighting, completion, navigation, definition extraction/inlining, and Rust plugin integration.
  \item Provides live preview -- test grammar files by dynamically highlighting user code according to the grammar.
  \item Supports exporting the highlighted user code to HTML format.
\end{itemize}

% \datedsubsection{\textbf{Julia-IntelliJ}}{\url{https://github.com/JuliaEditorSupport/julia-intellij}}
% Julia plugin for JetBrains IDEs
% \begin{itemize}
% \item Semantic-based highlighting, quick fixes, completion, parameter hint, special input mode for Unicode characters.
% \item Use Markdown plugin to highlight doc strings, provides REPL and SciView (showing the output of Plot libraries).
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

%% \section{\faHeartO\ Achievements}
%% \datedline{}{Aug. 2017}

\section{Skills}
\begin{itemize}[parsep=0.25ex]
  \item \textbf{Programming Languages}:
    \textbf{multilingual} (not limited to any specific language),
    and especially experienced in Java/Kotlin/Rust/C\#/Agda/Haskell,
    comfortable with Dart/C/C++/F\#/F$\star$/Idris/Perl/Arend (in random order).

  % compiler theories
  \item \textbf{Compilers}:
    understand various program representations such as Control Flow Graphs
    and A-Normal Form.

  % language Kotlin
  \item \textbf{Kotlin/Java}:
    \textbf{4 years} of experience,
    % \textbf{4} projects collected in
    % \href{https://kotlin.link/?q=ice} {Awesome Kotlin},
    familiar with JNI, Gradle, and Swing,
    understand Contract DSL and Kotlin coroutines,
    did some code analysis with Kotlin's compiler.

  \item \textbf{Type System}:
    understand Martin-L\"{o}f Type Theory, coinduction and Cubical Type Theory,
    currently studying Homotopy Type Theory,
    familiar with Idris, Agda (\textbf{2 years} of experience, contributor), F$\star$, Arend and some Coq.

  % \item \textbf{JetBrains MPS}:
  %   understand concepts and applications of \textbf{Language-Oriented Programming}.

  \item \textbf{IDE Toolings}:
    \textbf{3 years} of experience,
    familiar with the IntelliJ Platform infrastructure and overall
    architecture (created the
    \href{https://plugins.jetbrains.com/plugin/10413}
         {Julia plugin},
    \href{https://plugins.jetbrains.com/plugin/12176}
         {DTLC plugin},
    \href{https://plugins.jetbrains.com/plugin/12046}
         {Pest plugin} and many others), also have experience with Eclipse/SonarQube.

  % % platforms I am familiar with
  % \item \textbf{Mobile Development}:
  %   \textbf{2 years} of experience,
  %   Android (Java, Kotlin (Anko)), Fuchsia (Flutter).

  \item \textbf{Developing Tools}:
    can adapt to any editors/OSs, usually use JetBrains IDEs and Emacs under Ubuntu
    and Windows Subsystem of Linux.
    % have experience with team tools like YouTrack, Jira, GitHub, BitBucket, Coding.net, Tower.
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

\section{Miscellaneous}
\begin{itemize}[parsep=0.25ex]
  \item Some profile links (please use a PDF reader with web link support):
    \href{https://bintray.com/ice1000}{Bintray profile} (for publishing JVM libraries)
  , \href{https://crates.io/users/ice1000}{Crates.io profile} (for publishing Rust libraries)
  , \href{https://plugins.jetbrains.com/author/10a216dd-c558-4aaf-aa8a-723f431452fb}
    {IntelliJ Plugin developer profile}
  , \href{https://personal.psu.edu/yqz5714/}{Research Statement}
  %% \item Books about formal verification I've written: \url{https://github.com/ice1000/Books}
  \item Languages: English - fluent (TOEFL 100), Chinese - native speaker
  %% \item Opensource contributions: \url{https://ice1000.org/opensource-contributions/} \\
  %%   pull-requested (functional improvements) to organizations like \textit{Microsoft, JetBrains, Ruby, Dropbox, PingCAP, TiKV},
  %%   projects like \textit{agda, imgui, shields.io, intellij-solidity, IntelliJ-EmmyLua, intellij-haskell}
  \item Opensource Contributions: \url{https://ice1000.org/opensource-contributions/}
    % member of \textsf{JuliaEditorSupport}, \textsf{agda}, \textsf{pest-parser}, \textsf{EmmyLua} and more,
    contributed to \textsf{agda, KaTeX, shields.io, raft-rs, grpc-rs, intellij-solidity, intellij-haskell,
    intellij-rust, rust-analyzer}
    and other projects
    % (apart from organization projects)
  \item StackOverflow: \url{https://tinyurl.com/y5cmw3dz},
    3000+ reputations, also active on \href{https://stackexchange.com/users/9532102/} {other StackExchange sites}
  % https://raw.githubusercontent.com/ice1000/resume/master/resume.pdf
  \item Get the latest version of this resume: \url{https://tinyurl.com/y8xdlfug}
  % https://raw.githubusercontent.com/ice1000/resume/master/resume-elab.pdf
  \item Get the a more complete version of this resume (if you're interested in me):
    \url{https://tinyurl.com/y2v59t36}
  \item \textbf{1 dan} on
    \href{https://www.codewars.com/users/ice1000} {CodeWars},
    ranked \#31 on the whole site, primarily in Haskell, Agda and Idris
  \item Love making friends
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}

